Large-scale harmonic patterns clustering

### 2010-03-21 Paper/Paper.tex
new black and white figures
improved

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{code}
\end{center}
\caption{\small{A typical code from a codebook of size $200$. 
Patterns represented
$2$ bars and the pattern length was set to $16$.
BLACK AND WHITE VERSION COMING.
}}
\label{fig:code}
\end{figure}

\subsection{Cowbell Dataset}
We have $43,300$ songs, giving  $3,720,091$ non zero bars, a bar usually 
contains $4$ beats. WHERE DOES THIS DATA COMES FROM? GIFT FROM EN?

@@

See Figure \ref{fig:cluster}.

@@

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.6\columnwidth]{code}
\end{center}
\caption{\small{A typical code from a codebook of size $200$. 
Patterns represented
$2$ bars and the pattern length was set to $16$.
BLACK AND WHITE VERSION COMING.
}}
\label{fig:code}
\end{figure}

\subsection{Cowbell Dataset}
We have $43,300$ songs, giving  
%$\bf{3,720,091}$ 
$\mathbf{3.7}$\textbf{M} 
non zero bars, a bar usually 
contains $4$ beats. WHERE DOES THIS DATA COMES FROM? GIFT FROM EN?

@@

See Figure \ref{fig:cluster} and \ref{fig:cluster_diff}.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{close_patterns_diff}
\end{center}
\caption{\small{Cluster around the pattern and the difference of both.}}
\label{fig:cluster_diff}
\end{figure}
